Using simulation to optimize the sampling design of fisheries-independent trawl surveys

### 2018-07-12 analysis/paper/sim_survey_paper.Rmd
Add 3D wireframe figure

|      **Parameter name** |      **Symbol** |                                       **Setting** |
|:----------------------- | :-------------- | :------------------------------------------------ |
|             Set density |      $D_{sets}$ |    0.0005, 0.001, 0.002, 0.005, 0.01 sets / km^2^ |
|  Length sampling effort |   $M_{lengths}$ |        5, 10, 20, 50, 100, 500, 100 lengths / set |
|     Age sampling effort |      $M_{ages}$ |   2, 5, 10, 20, 50 ages / length group / division |

@@

>>>>

|      **Parameter name** |      **Symbol** |                                       **Setting** |
|:----------------------- | :-------------- | :------------------------------------------------ |
|             Set density |      $D_{sets}$ |    0.0005, 0.001, 0.002, 0.005, 0.01 sets / km^2^ |
|  Length sampling effort |   $M_{lengths}$ |       5, 10, 20, 50, 100, 500, 1000 lengths / set |
|     Age sampling effort |      $M_{ages}$ |   2, 5, 10, 20, 50 ages / length group / division |

@@

```{r error_fig, fig.height = 3, fig.width = 8.5, results = "hide"}

trellis_theme <- list(
  box.3d = list(col = "darkgrey"), 
  axis.line = list(col = "transparent"),
  strip.background = list(col = "transparent"), 
  strip.border = list(col = "transparent"),
   layout.heights = list(
        top.padding = 0,
        main.key.padding = 0,
        key.axis.padding = 0,
        axis.xlab.padding = 0,
        xlab.key.padding = 0,
        key.sub.padding = 0,
        bottom.padding = -5
    ),
    layout.widths = list(
        left.padding = 0,
        key.ylab.padding = 0,
        ylab.axis.padding = 0,
        axis.key.padding = 0,
        right.padding = 1
    )
)

zscale_format <- function(lim, logsc = FALSE, ...) {
    ans <- zscale.components.default(lim, logsc = logsc, ...)
    ans$left$labels$labels <- si(ans$left$labels$at)
    ans
}

d <- merge(sim$surveys, sim$age_strat_error_stats, by = "survey")
# d <- d[d$set_den != 0.0005, ]
d <- d[d$set_den %in% c(0.0005, 0.002, 0.01)]
set_den <- sort(unique(d$set_den))
d$set_den <- factor(d$set_den)
options(scipen = 999)
labs <- sapply(seq_along(set_den), function(i) as.expression(bquote(D[sets] == .(set_den[i]))), 
               USE.NAMES = FALSE)
zlabs <- list(at = pretty(d$RMSE), labels = si(pretty(d$RMSE)))

pdf("analysis/paper/figures/error_wireframe.pdf", height = 3, width = 8.5)

p <- wireframe(RMSE ~  lengths_cap * ages_cap | set_den, data = d,
          as.table = TRUE, drape = TRUE, col = "white", lwd = 0.5,
          strip = strip.custom(factor.levels = labs),
          scales = list(arrows = FALSE, cex = 0.7, z = zlabs),
          col.regions = viridis::viridis(100),
          screen = list(z = 230, x = 300), 
          xlab = list(expression(M[lengths]), rot = 25), 
          ylab = list(expression(M[ages]), rot = -15), 
          zlab = list("RMSE", rot = 95),
          colorkey = list(labels = zlabs, height = 0.6,
                          axis.line = list(col = "darkgrey")),
          par.settings = trellis_theme)
p <- update(p, layout = c(3, 1))
p

dev.off()

p
